Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-04-16 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{abstract}
NASA recently announced the Habitable Worlds Observatory (HWO), a coronagraphic mission to detect rocky planets in habitable zones, establish their habitability, and search for biosignatures. 
%Numerous instrumental and observational challenges have still to be overcome to design a coronagraphic mission with that goal. After a research phase aiming at the detection of a few tens of exo-Earth in the habitable zone, the Habitable Worlds Observatory will use its spectroscopic and polarimetric capabilities to probe these planets' atmosphere and surface properties. 
Surface liquid water is central to the definition of planetary habitability.
%
Photometric and polarimetric phase variations can show the presence of specularly reflecting oceans on exoplanets, in addition to being sensitive to rainbows and other cloud scattering effects. 
%
Direct imaging missions are optimised to detect planets near quadrature, which may obscure some of the phases at which these features are strongest. 
%
The range of scattering phases accessible for an exoplanet can be limited by its orbital inclination or the coronagraph's inner working angle. 
%
Planets that orbit close to edge-on have accessible phase angles limited by obscuration by the coronagraph. 
%
We use the list of target stars for the Habitable Worlds Observatory to estimate the number of exo-Earths that could be searched for non-Lambertian scattering phenomena. 
%
We find that exo-Earths in systems listed in this Habitable Worlds Observatory catalog will have a detectable Rayleigh scattering peak. 
%
The glint signature at planetary phase angles of 
%$\sim$50--70$^\circ$ 
$\sim$110--130$^\circ$ would be accessible to the Habitable Worlds Observatory in $\sim$14 systems, and the rainbow of water clouds at phases of 140--160$^\circ$ would be accessible in $\sim$42 systems, assuming a 62\,mas inner working angle (\IWA; 3$\lambda/D$ for a 6-m telescope at 600nm).
%
Increasing the \IWA to 2$\lambda/D$, increases the number of systems with detectable rainbows and glints by factors of roughly 2 and 3, respectively.
%
The number of systems in which an exo-Earth could be searched for these scattering phenomena increases with orbital eccentricity and scales approximately inversely with \IWA.     \end{abstract}

@@

%--------------------------------------------------------------------------------
\begin{figure*}%[t]
   \centering
   \includegraphics[width=\linewidth]{figures/Fig1IWAPol.png}
   \caption{BOTT PLOT this is a holder until Kim updates the figure}
    \label{fig:bottplot}
\end{figure*}
%--------------------------------------------------------------------------------

@@

The Extreme Coronagraph for Living Planetary Systems (ECLIPS) coronograph for LUVOIR was a proposed \SIrange{200}{2000}{\nano\meter} instrument for exoplanet characterisation, with a similar coronagraph operating between \num{450} and \SI{1800}{\nano\meter} planned for HabEx.
%
POLLUX, a proposed UV instrument for the LUVOIR study could also detect  polarised light from hot Jupiters at \SI{300}{\nano\meter} \citep{Bouret2018_pollux}.
%
However, because of the challenges associated with the design of a coronagraph in the UV, it appears to be unlikely that \hwo will include a UV high-contrast instrument sensitive to Earth-like planets.

@@

In this paper, we quantify the planetary phase angles that would be accessible for direct observations for hypothetical terrestrial planets orbiting in the habitable zones of HabWorlds target stars.
%
In \S 2.1, we describe the target list, in \S 2.2 we derive expressions for the range of phase angles given a few different limits, in \S 2.3, we describe Monte Carlo simulations to marginalize over the unknown orbital inclination and eccentricity of planets in these systems, and in \S 2.4, we outline how the planet/star contrast changes as a function of the planet's orbital phase.  
%
We present and discuss our results in \S 3 and conclude in \S 4. 
%the   the way that inclination and coronagraph inner working angle can limit the accessible phase angles  
% We minimally explore the contrast ratio as we are primarily exploring whether these scattering angles are reachable with inner working angle and outer working angle considered.

@@

\subsection{\hwo\ and Stellar Sample}
%\textcolor{blue}{Merge the 2 sections here into "Assumed technical specifications and sample"? I don't think this needs to be 2 subsections}
\hwo\ is still in the early stages of development, and the exact telescope and instrument design is as of yet undecided. 
%
In this work, we assume a \SI{6}{\meter} primary mirror, which is the currently favoured design for the observatory.
%
The observatory will utilise a coronagraph to suppress the stellar light and facilitate high-contrast observations of faint accompanying exoplanet. 
%
The \IWA{} of the coronagraph is currently undecided and will be driven by both the science requirements and technological limitations. 
%In this work, we investigate the scattering phase coverage obtainable for several choices for the \IWA\ of the observatory. 
%We also consider the Outer Working Angle (OWA) but for most targets this is not a limiting factor. 
%From the HabWorlds report. Inner Working Angle: The IWA defines the region near the star that cannot be accessed for direct imaging due to a coronagraphic mask, starshade obscuration, or an interferometric null. It depends on the architecture of the telescope, the starlight suppression system used, and the observation wavelength. While a nominal value could be defined by making assumptions about the design for Habitable Worlds Observatory, we choose instead to derive the IWA from the star list itself and Astro2020’s requirement that ~100 cumulative habitable zones be surveyed by direct imaging. As shown in the main table, an IWA near ~70 mas will be needed to access ~100 cumulative habitable zones, and would need to be achieved at all wavelengths of interest for spectral characterization. For any specific telescope and starlight suppression system architecture the IWA is typically proportional to wavelength; thus, the number of accessible HZs will strongly decrease as IWA(lambda) increases.
For ease of comparison, \cref{tab:IWA_OWA} lists the angular separations corresponding to multiples of $\lambda / D$ for a \SI{6}{\meter} telescope at representative visible and near infrared wavelengths of $\lambda = \SI{600}{\nano\meter}$ and $\SI{1}{\micro\meter}$.

@@

\hwo\ is currently envisioned to observe the stars stated in the NASA Exoplanet Exploration Program's Mission Star List for the Habitable Worlds Observatory.
%
\footnote{\url{https://exoplanets.nasa.gov/internal_resources/2645_NASA_ExEP_Target_List_HWO_Documentation_2023.pdf}}
%
This list comprises $\sim$160 stars, the majority of which are Sun-like dwarfs; 66~F~dwarfs, 55~G~dwarfs, 40~K~dwarfs, and 3~M~dwarfs.
%
The target list is constructed assuming a maximum planet magnitude of $R_c = 31$ and a contrast floor of \num{2.5e-11}. 
%with an occurrence rate of rocky planets in the optimistic habitable zone to be $\eta_{\oplus}$ = 0.24 \citep{decadal}. 
The corresponding adopted habitable zone limits are a semi-major axis of \SIrange{0.95}{1.67}{\au} for a solar twin, planet sizes between \SIrange{0.8}{1.4}{} Earth radii, and for non-solar stars, scale as square root of the bolometric luminosity normalized to the Sun. 
%
This range of orbital separation corresponds to the \enquote{conservative habitable zone} \citep{kasting93, kopparapu13}. 
%
The authors of the report determined that these are the nearby stars (maximum distance \SI{25}{\parsec}) for which exo-Earths would be the most observable for an imaging survey of habitable zones with a \SI{6}{\meter} telescope.

@@

\begin{figure}
    \centering
    \includestandalone{tikz/annotated-orbit}
    \caption{
        An illustration of an edge-on circular orbit showing that the coronagraph can obscure the exoplanet at high and low scattering phase angles.
        %
        This can prevent observations of scattering phenomena which could be used to indicate the habitability and atmospheric composition of the exoplanet. 
        %\timmy{Maybe mention that this is a simplified illustration with a circular orbit, plus we are basically looking at an edge-on system?}
    }
    \label{fig:annotated-orbit}
\end{figure}

@@

\Cref{fig:scatterplot} shows $\Delta \varphi$ for the systems in the \hwo\ target list, assuming an IWA of \SI{62}{\mas} ($3 \lambda / D$ coronagraph at $\SI{600}{\nano\meter}$). 
\timmy{60 (as in the abstract), or 62?}
%
%This assumes each planet has a semi-major axis such that it receives an Earth-equivalent instellation, which is provided in the input star list.
%
For edge-on circular orbits, it will be possible to observe Rayleigh scattering for all targets and rainbows will be accessible in some cases.

@@

For each star on the \hwo\ target list, we generate $1000$  hypothetical habitable planets at the Earth-equivalent-flux semi-major axis. 
%
The orbital inclinations are randomly drawn from a distribution uniform in $\cos i$. 
%
We then use \cref{eq:Delta_phi_max} to determine the range of accessible scattering phase angles for each hypothetical planet.
%
The solid lines in \cref{fig:betaallofit} show the cumulative distribution of the maximum and minimum accessible scattering phase angles normalised to the total number of systems in \hwo\ target list, depending on the choice of inner working angle.

@@

\subsubsection{Eccentric randomly inclined orbits}
\label{sec:eccentric}
We repeat the Monte Carlo simulation from \cref{sec:circular} assuming the orbital eccentricity follows a beta distribution with shape parameters $a=0.867$ and $b=3.03$ \citep{2013MNRAS.434L..51K}. 
%
We randomly drew 1000 random orbits for each star and determined the sky-projected orbits following, e.g., \cite{2010exop.book...15M}. Eccentricities were drawn from the beta distribution, and inclinations were uniform in $\cos i$. \Cref{fig:ball-o-yarn} shows a sample of the generated orbits with the filtered \IWA's
%
%Each plot has been scaled such that the habitable zone occupies the same radius, hence the \IWA's vary in apparent size compared to the orbit.
%
We then calculated the minimum and maximum accessible scattering phase angles for of \IWA's of 21, 42, 63 and 84 mas which correspond to 1, 2, 3 and 4 times $\lambda / D$ at $\SI{600}{\nano\meter}$.
%
The dashed lines in \cref{fig:betaallofit} shows the normalised cumulative distribution of the accessible angles for each of the \IWA, when accounting for orbital eccentricity.
%
We also calculate which targets would be observable at the scattering phase angles where ocean glint, rainbows, or the Rayleigh peak occur.
%
The cumulative distribution over \IWA\ of the number of systems, normalised to the total number of systems, where each scattering phenomena is visible is shown in \cref{fig:accessible_phase_angles}.
%

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/Contrast_vs_separation_inclination_angle_90.pdf}
   \caption{
    The reflected light contrast and orbital separation of an Earth-like planet with an ocean surface and patchy clouds over a planetary orbit assuming an orbital inclination of $90^\circ$ for the stars $\alpha$ Cen A, $\epsilon$ Eri and Lalande 21185.
    %
    The solid line indicates the contrast in unpolarised light with the contrast at quadrature marked by a solid dot.
    %
    The polarised component is indicated by the colored dots for which the color represents the scattering phase angle from quadrature.
    %
    The light grey points show the quadrature contrasts of the other targets in the star list and the dashed lines indicate $1,2$ and $3$ times the \IWA\ for \hwo.
    }
    \label{fig:contrasts}
    \script{plot_contrasts.py}
\end{figure*}

@@

The accessible scattering phase angles is not the factor that needs to be considered when determining what scattering features are observable.
%
The contrast of the planet is also an important factor to consider.
%
\cref{fig:contrasts} shows approximate contrast curves for three of the stars in the \hwo\ target list assuming edge-on orbits.
%
The over all contrast varies significantly for each system and throughout the orbit.
%
The observability of these planets will depend on the star light suppression of the coronagraph which is influenced by its \IWA{}.
%
It is not possible to predict how much the state of the art of coronagraphy will have advanced by the time \hwo{} is built.
%
However, when its design is being finalised, it will be important to consider both the accessible scattering phase angles and contrast limits when deciding on the \IWA{} of the coronagraph, if these features are to be observed.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/ball_of_yarn.pdf}  
    \caption{
        %Are we putting all of these somewhere?  Its prob about 7 pages worth in total?
        Random examples of the eccentric orbits generated for the stellar sample.
        %
        The orbits are scaled by the Earth-equivalent flux distance. 
        %
        The concentric circles marked by the dashed lines indicate inner working angles of 20.6, 41.3, 61.9, and \SI{82.5}{\mas}, corresponding to 1, 2, 3, and 4\,$\lambda / D$ respectively (assuming $\lambda = \SI{600}{\nano\meter}$ and $D = \SI{6}{\meter}$).
        %
        The figure illustrates that the \IWA\ can significantly affect the range of scattering phases observable with each orbit.
    }
    \label{fig:ball-o-yarn}
    \script{make_yarn_plot.py} % most awesome command in this paper.  This knitter approves.
\end{figure*}

>>>>

\begin{abstract}
NASA recently announced the Habitable Worlds Observatory (HWO), a coronagraphic mission to detect rocky planets in habitable zones, establish their habitability, and search for biosignatures. 
%Numerous instrumental and observational challenges have still to be overcome to design a coronagraphic mission with that goal. After a research phase aiming at the detection of a few tens of exo-Earth in the habitable zone, the Habitable Worlds Observatory will use its spectroscopic and polarimetric capabilities to probe these planets' atmosphere and surface properties. 
Surface liquid water is central to the definition of planetary habitability.
%
Photometric and polarimetric phase variations can show the presence of specularly reflecting oceans on exoplanets, in addition to being sensitive to rainbows and other cloud scattering effects. 
%
Direct imaging missions are optimised to detect planets near quadrature, which may obscure some of the phases at which these features are strongest. 
%
The range of scattering phases accessible for an exoplanet can be limited by its orbital inclination or the coronagraph's inner working angle. 
%
Planets that orbit close to edge-on have accessible phase angles limited by obscuration by the coronagraph. 
%
We use the list of target stars for the Habitable Worlds Observatory to estimate the number of exo-Earths that could be searched for non-Lambertian scattering phenomena. 
%
We find that exo-Earths in systems listed in this Habitable Worlds Observatory catalog will have a detectable Rayleigh scattering peak. 
%
The glint signature at planetary phase angles of 
$\sim$50--70$^\circ$ 
%\sim$110--130$^\circ$ 
would be accessible to the Habitable Worlds Observatory in $\sim$14 systems, and the rainbow of water clouds at phases of 140--160$^\circ$ would be accessible in $\sim$42 systems, assuming a 62\,mas inner working angle (\IWA; 3$\lambda/D$ for a 6-m telescope at 600nm).
%
Increasing the \IWA to 2$\lambda/D$, increases the number of systems with detectable rainbows and glints by factors of roughly 2 and 3, respectively.
%
The number of systems in which an exo-Earth could be searched for these scattering phenomena increases with orbital eccentricity and scales approximately inversely with \IWA{}.    \end{abstract}

@@

%--------------------------------------------------------------------------------
\begin{figure*}%[t]
   \centering
   \includegraphics[width=\linewidth]{figures/Fig1IWAPol.png}
   \caption{An illustration of phase curves for two homogeneous planets in an edge on system with oceans and an Earth-like atmosphere. The cloudy scenario includes an Earth-like water cloud deck at low altitudes. Below the plot, the features that the phase angles and scattering angles are most sensitive to are shown. In reality, as can be seen by the examples above, these features overlap.  Throughout the paper we approximate feature sensitivity ranges as those that capture the rise an fall of peaks in polarized light for most habitable zone species in the UV, Optical, and IR (scattering angles: glint $\sim$50--70$^\circ$; rainbow $\sim$140--160$^\circ$}; Rayleigh narrow of quadrature, and other forward and backscattering effects at the widest and narrowest scattering angles).
    \label{fig:bottplot}
\end{figure*}
%--------------------------------------------------------------------------------

@@

The Extreme Coronagraph for Living Planetary Systems (ECLIPS) coronograph for LUVOIR was a proposed \SIrange{200}{2000}{\nano\meter} instrument for exoplanet characterisation, with a similar coronagraph operating between \num{450} and \SI{1800}{\nano\meter} planned for HabEx.
%
POLLUX, a proposed UV instrument for the LUVOIR study could also detect  polarised light from hot Jupiters at \SI{300}{\nano\meter} \citep{Bouret2018_pollux}.
%
However, because of the challenges associated with the design of a coronagraph in the UV, it appears to be unlikely that \hwo{} will include a UV high-contrast instrument sensitive to Earth-like planets.

@@

In this paper, we quantify the planetary phase angles that would be accessible for direct observations for hypothetical terrestrial planets orbiting in the habitable zones of HabWorlds (HWO) target stars.
%
In \S 2.1, we describe the target list, in \S 2.2 we derive expressions for the range of phase angles given a few different limits, in \S 2.3, we describe Monte Carlo simulations to marginalize over the unknown orbital inclination and eccentricity of planets in these systems, and in \S 2.4, we outline how the planet/star contrast changes as a function of the planet's orbital phase.  
%
We present and discuss our results in \S 3 and conclude in \S 4. It is important to note that the phases for each feature throughout this paper are approximate, that features overlap, and that the maximum peak can vary with composition and wavelength.
%the   the way that inclination and coronagraph inner working angle can limit the accessible phase angles  
% We minimally explore the contrast ratio as we are primarily exploring whether these scattering angles are reachable with inner working angle and outer working angle considered.

@@

\subsection{\hwo{} and Stellar Sample}
%\textcolor{blue}{Merge the 2 sections here into "Assumed technical specifications and sample"? I don't think this needs to be 2 subsections}
\hwo{} is still in the early stages of development, and the exact telescope and instrument design is as of yet undecided. 
%
In this work, we assume a \SI{6}{\meter} primary mirror, which is the currently favoured design for the observatory.
%
The observatory will utilise a coronagraph to suppress the stellar light and facilitate high-contrast observations of faint accompanying exoplanet. 
%
The \IWA{} of the coronagraph is currently undecided and will be driven by both the science requirements and technological limitations. 
%In this work, we investigate the scattering phase coverage obtainable for several choices for the \IWA{} of the observatory. 
%We also consider the Outer Working Angle (OWA) but for most targets this is not a limiting factor. 
%From the HabWorlds report. Inner Working Angle: The IWA defines the region near the star that cannot be accessed for direct imaging due to a coronagraphic mask, starshade obscuration, or an interferometric null. It depends on the architecture of the telescope, the starlight suppression system used, and the observation wavelength. While a nominal value could be defined by making assumptions about the design for Habitable Worlds Observatory, we choose instead to derive the IWA from the star list itself and Astro2020’s requirement that ~100 cumulative habitable zones be surveyed by direct imaging. As shown in the main table, an IWA near ~70 mas will be needed to access ~100 cumulative habitable zones, and would need to be achieved at all wavelengths of interest for spectral characterization. For any specific telescope and starlight suppression system architecture the IWA is typically proportional to wavelength; thus, the number of accessible HZs will strongly decrease as IWA(lambda) increases.
For ease of comparison, \cref{tab:IWA_OWA} lists the angular separations corresponding to multiples of $\lambda / D$ for a \SI{6}{\meter} telescope at representative visible and near infrared wavelengths of $\lambda = \SI{600}{\nano\meter}$ and $\SI{1}{\micro\meter}$.

@@

\hwo{} is currently envisioned to observe the stars stated in the NASA Exoplanet Exploration Program's Mission Star List for the Habitable Worlds Observatory.
%
\footnote{\url{https://exoplanets.nasa.gov/internal_resources/2645_NASA_ExEP_Target_List_HWO_Documentation_2023.pdf}}
%
This list comprises $\sim$160 stars, the majority of which are Sun-like dwarfs; 66~F~dwarfs, 55~G~dwarfs, 40~K~dwarfs, and 3~M~dwarfs.
%
The target list is constructed assuming a maximum planet magnitude of $R_c = 31$ and a contrast floor of \num{2.5e-11}. 
%with an occurrence rate of rocky planets in the optimistic habitable zone to be $\eta_{\oplus}$ = 0.24 \citep{decadal}. 
The corresponding adopted habitable zone limits are a semi-major axis of \SIrange{0.95}{1.67}{\au} for a solar twin, planet sizes between \SIrange{0.8}{1.4}{} Earth radii, and for non-solar stars, scale as square root of the bolometric luminosity normalized to the Sun. 
%
This range of orbital separation corresponds to the \enquote{conservative habitable zone} \citep{kasting93, kopparapu13}. 
%
The authors of the report determined that these are the nearby stars (maximum distance \SI{25}{\parsec}) for which exo-Earths would be the most observable for an imaging survey of habitable zones with a \SI{6}{\meter} telescope.

@@

\begin{figure}
    \centering
    \includestandalone{tikz/annotated-orbit}
    \caption{
        An illustration of an edge-on circular orbit showing that the coronagraph can obscure the exoplanet at high and low scattering phase angles.
        %
        This can prevent observations of scattering phenomena which could be used to indicate the habitability and atmospheric composition of the exoplanet. The phase angle, $\varphi$, is shown in red and is the complement to the scattering angle in edge on systems.
        %\timmy{Maybe mention that this is a simplified illustration with a circular orbit, plus we are basically looking at an edge-on system?}
    }
    \label{fig:annotated-orbit}
\end{figure}

@@

\Cref{fig:scatterplot} shows $\Delta \varphi$ for the systems in the \hwo{} target list, assuming an IWA of \SI{62}{\mas} ($3 \lambda / D$ coronagraph at $\SI{600}{\nano\meter}$). 
\timmy{60 (as in the abstract), or 62?}
%
%This assumes each planet has a semi-major axis such that it receives an Earth-equivalent instellation, which is provided in the input star list.
%
For edge-on circular orbits, it will be possible to observe Rayleigh scattering for all targets and rainbows will be accessible in some cases.

@@

For each star on the \hwo{} target list, we generate $1000$  hypothetical habitable planets at the Earth-equivalent-flux semi-major axis. 
%
The orbital inclinations are randomly drawn from a distribution uniform in $\cos i$. 
%
We then use \cref{eq:Delta_phi_max} to determine the range of accessible scattering phase angles for each hypothetical planet.
%
The solid lines in \cref{fig:betaallofit} show the cumulative distribution of the maximum and minimum accessible scattering phase angles normalised to the total number of systems in \hwo{} target list, depending on the choice of inner working angle.

@@

\subsubsection{Eccentric randomly inclined orbits}
\label{sec:eccentric}
We repeat the Monte Carlo simulation from \cref{sec:circular} assuming the orbital eccentricity follows a beta distribution with shape parameters $a=0.867$ and $b=3.03$ \citep{2013MNRAS.434L..51K}. 
%
We randomly drew 1000 random orbits for each star and determined the sky-projected orbits following, e.g., \cite{2010exop.book...15M}. Eccentricities were drawn from the beta distribution, and inclinations were uniform in $\cos i$. \Cref{fig:ball-o-yarn} shows a sample of the generated orbits with the filtered \IWA's
%
%Each plot has been scaled such that the habitable zone occupies the same radius, hence the \IWA's vary in apparent size compared to the orbit.
%
We then calculated the minimum and maximum accessible scattering phase angles for of \IWA's of 21, 42, 63 and 84 mas which correspond to 1, 2, 3 and 4 times $\lambda / D$ at $\SI{600}{\nano\meter}$.
%
The dashed lines in \cref{fig:betaallofit} shows the normalised cumulative distribution of the accessible angles for each of the \IWA, when accounting for orbital eccentricity.
%
We also calculate which targets would be observable at the scattering phase angles where ocean glint, rainbows, or the Rayleigh peak occur.
%
The cumulative distribution over \IWA{} of the number of systems, normalised to the total number of systems, where each scattering phenomena is visible is shown in \cref{fig:accessible_phase_angles}.
%

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/Contrast_vs_separation_inclination_angle_90.pdf}
   \caption{
    The reflected light contrast and orbital separation of an Earth-like planet with an ocean surface and patchy clouds over a planetary orbit assuming an orbital inclination of $90^\circ$ for the stars $\alpha$ Cen A, $\epsilon$ Eri and Lalande 21185.
    %
    The solid line indicates the contrast in unpolarised light with the contrast at quadrature marked by a solid dot.
    %
    The polarised component is indicated by the colored dots for which the color represents the scattering phase angle from quadrature.
    %
    The light grey points show the quadrature contrasts of the other targets in the star list and the dashed lines indicate $1,2$ and $3$ times the \IWA{} for \hwo.
    }
    \label{fig:contrasts}
    \script{plot_contrasts.py}
\end{figure*}

@@

The accessible scattering phase angles is not the factor that needs to be considered when determining what scattering features are observable.
%
The contrast of the planet is also an important factor to consider.
%
\cref{fig:contrasts} shows approximate contrast curves for three of the stars in the \hwo{} target list assuming edge-on orbits.
%
The over all contrast varies significantly for each system and throughout the orbit.
%
The observability of these planets will depend on the star light suppression of the coronagraph which is influenced by its \IWA{}.
%
It is not possible to predict how much the state of the art of coronagraphy will have advanced by the time \hwo{} is built.
%
However, when its design is being finalised, it will be important to consider both the accessible scattering phase angles and contrast limits when deciding on the \IWA{} of the coronagraph, if these features are to be observed.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/ball_of_yarn.pdf}  
    \caption{
        %Are we putting all of these somewhere?  Its prob about 7 pages worth in total?
        Random examples of the eccentric orbits generated for the stellar sample.
        %
        The orbits are scaled by the Earth-equivalent flux distance. 
        %
        The concentric circles marked by the dashed lines indicate inner working angles of 20.6, 41.3, 61.9, and \SI{82.5}{\mas}, corresponding to 1, 2, 3, and 4\,$\lambda / D$ respectively (assuming $\lambda = \SI{600}{\nano\meter}$ and $D = \SI{6}{\meter}$).
        %
        The figure illustrates that the \IWA{} can significantly affect the range of scattering phases observable with each orbit.
    }
    \label{fig:ball-o-yarn}
    \script{make_yarn_plot.py} % most awesome command in this paper.  This knitter approves.
\end{figure*}
